---
title: "R Project 1 - Hello R"
author: "Alison Cheek"
date: "September 8, 2021"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

Based on the help file, there are 1,846 rows and 3 columns in the datasaurus_dozen file.  
The three variables are: the x-values, y-values, and the dataset.


### Exercise 2

Plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

In my first attempts, I was selecting the chunk of code and running it to see that it worked correctly, but I kept getting an error message.  However, once I tried knitting it I saw it plotted out there.


```{r plot-star,fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

I've replaced the same code with the star_data variable.  The values are not too far off, meaning the correlation between the x and y in each data set are closer than I would have thought. 
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

My circle is more of an oval, and I am unsure if that is to do with the plot or that data, but I think it is the plot.

```{r plot-circle,fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation is in the negatives, like for the dino and star plots, but it is a much lower correlation number.

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)
